\documentclass[10pt,a4paper,ragged2e]{altacv}
\usepackage{multicol}
\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000
\geometry{left=2cm,right=11cm,marginparwidth=8cm,marginparsep=1.2cm,top=2cm,bottom=1.25cm}
\ifxetexorluatex
  \setmainfont{Carlito}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi
\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
\addbibresource{sample.bib}

\begin{document}
\name{Ethan Michel}
\tagline{Oberlin College}
% Cropped to square from https://en.wikipedia.org/wiki/Marissa_Mayer#/media/File:Marissa_Mayer_May_2014_(cropped).jpg, CC-BY 2.0
%\photo{3.3cm}{profile.jpg}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{ethanmichel303@gmail.com}
%   \phone{000-00-0000}
%  \mailaddress{Address, Street, 00000 County}
  \location{Boulder, CO}
%  \homepage{marissamayr.tumblr.com/}
%  \twitter{@marissamayer}
  \linkedin{https://www.linkedin.com/in/ethan-michel-0b926685}
%   \orcid{orcid.org/0000-0000-0000-0000} % Obviously making this up too. If you want to use this field (and also other academicons symbols), add "academicons" option to \documentclass{altacv}
}

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvsection[page1sidebar]{Work Experience}

\cvevent{Salesforce Developer Intern}{NuAge Experts A ConvergeOne Company }{June 2021 - Current}{Boulder, CO}

\begin{itemize}
    
\item Proposed and implemented a project to make custom data loading in development environments 90\% faster for non-technical users. Built a containerized full-stack application with Node.js, Typescript, PostgreSQL, and Docker, implementing industry standard security.

\item Led weekly check-ins with a developer who helped build a Javascript-based Salesforce package to integrate with the cloud application for the data loading project I proposed. Clarified project vision, answered Javascript technical questions, and collaboratively brainstormed how to improve the user experience with the software.

\item Collaborated with technical architect and project manager on a ground-up re-architecture effort for a managed services client, and led a migration of over 40 complex business processes from declarative tools to Apex (Java-based) code.

\end{itemize}

\divider

\cvevent{Software Engineer Intern}{SmartEtailing}{Aug -- Dec 2020}{Boulder, CO}
\begin{itemize}
\item Led a project to make the previously Windows-hosted legacy Coldfusion codebase compatible with Linux by making code changes and configuring servers. This enabled the migration of over 10 virtual machines from Windows to Linux.

\smallskip
\smallskip
\item Improved the merchant provisioning experience by creating an interactive Vue js feature utilizing Vuex state management. This made provisioning a new merchant 50\% faster.
\smallskip
\item Actively participated in daily stand ups, sprint planning, reviews, and retrospectives, and embraced scrum values.
\end{itemize}

\divider

\cvevent{Software Engineer Intern}{Environmental Dashboard}{June - Aug 2020}{Oberlin, OH}
\begin{itemize}
\item Created a custom feature that interpreted spreadsheets, allowing content managers to upload multiple records at once. This involved a database redesign, multiple layers of validation, and an interactive page allowing users to manipulate spreadsheet data and react to errors. Reduced the time users needed to upload batches of records by 75\%.
\item Independently managed and fixed multiple bugs in a full-stack codebase utilizing N-Tiered and MVC architectures without prior experience in PHP, APIs, or web development.
\end{itemize}

\end{document}
