\cvsection{Education}
\cvevent{B.A. in Computer Science}{Oberlin College  - 3.88 GPA}{Graduating December 2022}{}
\begin{itemize}
    \item John F Oberlin Scholarship: Awarded to top 10\% of incoming class.
    \item CS Teaching Assistant and Tutor for Intro to Computer Science and Data Structures classes.
    \item Member of the men's varsity soccer team.
    \item Peer Listener: Volunteer position to help struggling students through active listening and empathy. Took the two required introductory classes.
\end{itemize}
\cvsection{Technical Experience}
\textbf{Coursework}
\vspace*{-10px}
\begin{multicols*}{2}
\begin{itemize}
    \item Data Structures
    \item Systems Programming
    \item Discrete Mathematics
    \item Algorithms 
    \vfill\null
    \item Programming Abstractions
    \item Computer Architecture
    \item Operating Systems
    \item Vue - The Complete Guide (Udemy)
    
\end{itemize}
\end{multicols*}
%\vspace*{-10px}
\textbf{Languages}
\vspace*{-10px}
\begin{multicols}{2}
\begin{itemize}
    \item Java
    \item Python
    \item PHP
    \item SQL
    \item Javascript (Salesforce Certified)
\end{itemize}
\end{multicols}
% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

%\cvtag{Hard-working (18/24)} 
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}


%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}
\cvsection{Projects}
\begin{itemize}
    \item Built a full stack application for community college students to add and remove classes using Vue.js and Spring Boot.
    \item Developed an algorithm for estimating the density and health of algae to help a graduate student track algae growth for his project.
\end{itemize}

\cvsection{Achievements}
\smallskip
\begin{itemize}
\item Member of a team of four that took second place at the 2020 Denison University Programming Competition.
\item Three year captain of my high school varsity soccer team; led the team to our first ever state final.
\item Finalist and runner-up in high school for the Heart of a Warrior award, given to the senior who best embodies the school values of work ethic, integrity, and respect.
\end{itemize}
\cvproject{}
